PTFO 8-8695: Two Stars, Two Signals, No Planet

### 2020-06-12 paper/ms.tex
wordsmith

%\documentclass[12pt,twocolumn,tighten]{aastex62}
\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

The explanations that \replaced{are not yet}{have not yet been} ruled
out include {\it (i)} transiting clumps of \added{dust or }gas at the
Keplerian co-rotation radius; {\it (ii)} transits of enshrouded
protoplanets; {\it (iii)} occultations of \replaced{starspots}{hot and
cold spots on the stellar surface} by an optically thick disk.  The
first and last explanations have added appeal because they are
flexible enough to explain not only the transient and persistent-dip
M-dwarfs, but also the ``scallop shell'' M-dwarfs
\citep{stauffer_orbiting_2017}.  \replaced{Despite this appeal, the
possibility of distinct mechanisms explaining these distinct
variability classes remains open.}{ The model of hot and coldspot
occultations by an optically thick disk \citep{zhan_complex_2019} is a
qualitative inverse of the torus of circumstellar material: the
difference is whether to place the ``blobs'' that provide the needed
brightness contrast on the surface of the star, or at the co-rotation
radius.  In the spot occultation model, the observing geometry would
require an inner disk to be projected into a narrow band across the
stellar surface, in order to produce variations with sufficiently
short timescales.  The outer disk would need either to not be present,
or to be misaligned enough, and narrow enough, that it did not fall
along the line of sight. These combined requirements seem
geometrically contrived.  }

@@

\explain{Updated this paragraph to remove spot occultations by a disk as
a ``preferred explanation''.}
The physical mechanism that explains the transient and persistent flux
dips is unresolved. Our preferred explanation is that a clumpy torus of dust or gas is near the Keplerian co-rotation radius, and periodically occults the star.
The \added{chromaticity, out-of-eclipse variability, and} jumping orbital phase \replaced{disfavored}{of \ptfo\ all disfavor} the explanation of an enshrouded,
transiting protoplanet.  Though \ptfo\ may not be a planet,\deleted{ as we and
others had hoped,} understanding it and its analogs is a worthy
problem\replaced{.}\added{that seems likely to provide insight into how gas
and dust disperse from young protostellar disks.} \replaced{It might even}{Understanding
this process would, in turn,} teach us about the birth environments of the
majority of habitable-zone Earth-sized planets
\citep{dressing_occurrence_2013}.

>>>>

\documentclass[12pt,twocolumn,tighten]{aastex62}
%\documentclass[12pt,twocolumn,tighten,trackchanges]{aastex62}
\usepackage{amsmath,amstext,amssymb}
\usepackage[T1]{fontenc}
\usepackage{apjfonts}
\usepackage[figure,figure*]{hypcap}
\usepackage{graphics,graphicx}
\usepackage{hyperref}
\usepackage{natbib}
\usepackage[caption=false]{subfig} % for subfloat
\usepackage{enumitem} % for specific spacing of enumerate
\usepackage{epigraph}

@@

The explanations that \replaced{are not yet}{have not yet been} ruled
out include {\it (i)} transiting clumps of \added{dust or }gas at the
Keplerian co-rotation radius; {\it (ii)} transits of enshrouded
protoplanets; {\it (iii)} occultations of \replaced{starspots}{hot and
cold spots on the stellar surface} by an optically thick disk.  The
first and last explanations have added appeal because they are
flexible enough to explain not only the transient and persistent-dip
M-dwarfs, but also the ``scallop shell'' M-dwarfs
\citep{stauffer_orbiting_2017}.  \replaced{Despite this appeal, the
possibility of distinct mechanisms explaining these distinct
variability classes remains open.}{ The model of hot and coldspot
occultations by an optically thick disk \citep{zhan_complex_2019} is a
qualitative inverse of the torus of circumstellar material: the
difference is whether to place the ``blobs'' that provide the needed
brightness contrast on the surface of the star, or at the co-rotation
radius.  In the spot occultation model, the observing geometry would
require an inner disk to be projected into a narrow band across the
stellar surface, in order to produce variations with sufficiently
short timescales.  The outer disk would need to either not be present,
or to be misaligned enough, and narrow enough, that it did not fall
along the line of sight. These combined requirements seem
geometrically contrived.  }

@@

\explain{Updated this paragraph to remove spot occultations by a disk as
a ``preferred explanation''.}
The physical mechanism that explains the transient and persistent flux
dips is unresolved. Our preferred explanation is that a clumpy torus of dust or gas is near the Keplerian co-rotation radius, and periodically occults the star.
The \added{chromaticity, out-of-eclipse variability, and} jumping orbital phase \replaced{disfavored}{of \ptfo\ all disfavor} the explanation of an enshrouded,
transiting protoplanet.  Though \ptfo\ may not be a planet,\deleted{ as we and
others had hoped,} understanding it and its analogs is a worthy
problem\replaced{.}{ that seems likely to provide insight into how gas
and dust disperse from young protostellar disks.} \replaced{It might even}{Understanding
this process would, in turn,} teach us about the birth environments of the
majority of habitable-zone Earth-sized planets
\citep{dressing_occurrence_2013}.
